### 2017-06-28 R/msa.Rmd

```{r msamsa, eval = FALSE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
msaIDFile <- read.csv(system.file("join2.csv", package = "ITHIM"), stringsAsFactors = FALSE)
msaIDs <- msaIDFile$msaNHTS %>% unique
msaIDs <- msaIDs[!is.na(msaIDs)] %>% as.list
names(msaIDs) <- msaIDs
FList <- getPopulation(msaIDs)

@@

#msaIDs <- unique(NHTS.df$location)
#msaIDs <- as.character(msaIDs[msaIDs!="-1"])

@@

>>>>

```{r msamsa, eval = TRUE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
msaIDFile <- read.csv(system.file("join2.csv", package = "ITHIM"), stringsAsFactors = FALSE)
msaIDs <- msaIDFile$msaNHTS %>% unique
msaIDs <- msaIDs[!is.na(msaIDs)] %>% as.list
names(msaIDs) <- msaIDs
FList <- getPopulation(msaIDs)

@@

msaIDs <- unique(NHTS.df$location)
msaIDs <- as.character(msaIDs[msaIDs!="-1"])

@@

msaID.portland <- "6442"
FList[[msaID.portland]] %>% gather(sex,value,1:2) %>% mutate(ageClass=rep(rownames(FList[[msaID.portland]]),2)) %>% select(ageClass,sex,value) %>% write.csv(., file = "~/ITHIM/inst/F.portland.csv", quote = FALSE, row.names = FALSE)

rbind(MwtList[[msaID.portland]] %>% as.data.frame() %>% gather(sex,value,1:2) %>% mutate(ageClass=rep(rownames(FList[[msaID.portland]]),2)) %>% select(ageClass,sex,value) %>% mutate(mode = "walk"), MctList[[msaID.portland]] %>% as.data.frame() %>% gather(sex,value,1:2) %>% mutate(ageClass=rep(rownames(FList[[msaID.portland]]),2)) %>% select(ageClass,sex,value) %>% mutate(mode = "cycle")) %>% select(ageClass,sex,mode,value) %>% write.csv(., file = "~/ITHIM/inst/activeTransport.portland.csv", quote = FALSE, row.names = FALSE)
